Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case

### 2019-01-23 ICML-submission/empirical-comparison.tex
Fixes

We implemented
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples},
Algorithm~\ref{algorithm:kernelized} with
kernel~\eqref{equation:rational-kernel}, and the \textsc{Banditron} algorithm.
We generated strongly and weakly separable data sets with $K=3$ classes. The
data sets are shown in~\autoref{figure:strongly-and-weakly-separable-datasets}.
Although, the data sets are shown as two-dimensional, we used a third dimension,
the so-called \emph{constant feature}, i.e. a feature that for every example is
set to $1$. We added the constant feature so that
\autoref{figure:strongly-separable-dataset} is actually strongly lineraly
separable. For both data sets, the sample size is $T=5\times 10^6$ and the
margin is $\gamma=0.05$.

@@

We evaluated all three the algorithms on the two data sets. Since all three
algorithms are randomized, we run each algorithm $20$ times. \textsc{Banditron}
has exploration rate parameter $\epsilon$ for which we tried values $\epsilon
\in \{0.02, 0.01, 0.005, 0.002, 0.001, 0.0005 \}$. The average cumulative number
of mistakes up to round $t$ as a function $t$ are shown in
Figures~\ref{figure:number-of-mistakes-strongly-separable-dataset}
and~\ref{figure:number-of-mistakes-weakly-separable-dataset}.

>>>>

We implemented
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples},
Algorithm~\ref{algorithm:kernelized} with
kernel~\eqref{equation:rational-kernel}, and the \textsc{Banditron} algorithm.
We generated strongly and weakly separable data sets with $K=3$ classes. The
data sets are shown in~\autoref{figure:strongly-and-weakly-separable-datasets}.
Although, the data sets are shown as two-dimensional, we used a third dimension
that for every example is equal to $1$. In other words, we added the so-called
\emph{constant feature}. The constant feature is necessary so that
\autoref{figure:strongly-separable-dataset} is actually strongly lineraly
separable. For both data sets, the sample size is $T=5\times 10^6$ and the
margin is $\gamma=0.05$.

@@

We evaluated all three algorithms on the two data sets. Since all three
algorithms are randomized, we run each algorithm $20$ times. \textsc{Banditron}
has exploration rate parameter $\epsilon$ for which we tried values $\epsilon
\in \{0.02, 0.01, 0.005, 0.002, 0.001, 0.0005 \}$. The average cumulative number
of mistakes up to round $t$ as a function $t$ are shown in
Figures~\ref{figure:number-of-mistakes-strongly-separable-dataset}
and~\ref{figure:number-of-mistakes-weakly-separable-dataset}.
